We are excited to welcome you to BriGap-2, co-located with IWCS 2025, in Düsseldorf, Germany!\\

This second edition of the workshop on Bridges and Gaps between Formal and Computational Linguistics follows up on the first edition in 2022.
We have implemented a number of changes that we hope will reflect the diverse communities that we aim to bring together in this event.
In particular, we have worked towards designing an inclusive and welcoming submission policy, soliciting archival papers to be published in the ACL Anthology, non-archival abstracts describing work in progress, as well as presentations of already published articles that would be of interest to our audience.

We are especially proud of the success encountered in this second edition, with 11 publications presented at the workshop, 9 of which are included in these proceedings.
The works range across a number of topics, including but not limited to Dependent Type Semantics, the syntactic abilities of LLMs, Lexical Functional Grammer, as well as the use NLP systems for cognitive science.
We hope that future editions of the workshop will be able to build upon this success and continue to foster the diversity of topics addressed.

Beyond these 11 presentations, the workshop also includes two invited talks. 
Anna Rogers (ITU Copenhagen) will discuss data contamination in the age of LLMs, whereas Kees van Deemter (University of Utrecht) will address hallucinations and how to classify them.
Both keynotes provide valuable perspectives on pitfalls and caveats of modern NLP technology, and provide an excellent starting point for a broader discussion on how to build successful interactions between formal and computational linguistics.\\

The BriGap-2 workshop was made possible thanks to the financial support of RT LIFT2, a France-based research group aiming to bring together researchers in computational linguistics, formal linguistics, and field linguistics around shared questions, data, and tools.

We also want to thank our colleague Grégoire Winterstein, who helped us put together the workshop proposal before withdrawing from the organizing committee due to an excessive workload.\\\\

%Timothée Bernard, Timothee Mickus, Grégoire Winterstein, Program Chairs
Timothée Bernard, Timothee Mickus, Program Chairs
